Hydras \& Co.

### 2022-02-24 doc/gaia-chapter.tex
More uses of 'decide equality' tactic
add stuff in gaia-chapter.tex

@@

>>>>

\subsubsection{Canonical sequences and limits}

@@

\subsection{Accessibility in \texorpdfstring{$\epsilon_0$}{epsilon\_0}}

The library \href{../theories/html/gaia.GPaths.html}%
{\texttt{gaia.GPaths}} imports definitions and lemmas from
\href{../theories/html/hydras.Epsilon0.Paths.html}%
{\texttt{hydras.Epsilon0.Paths}}.

\subsubsection{Remark}
\label{sect:gaia-masking}

First, we import some definitions. When we import some constant \emph{Id} from {\texttt{hydras.Epsilon0.Paths}} the name
\emph{Id} is given to {\texttt{gaia.GPaths}}. In order to get
{\texttt{hydras.Epsilon0.Paths}}'s sense, please refer it as
\emph{Paths.Id}.
Sometimes, we rename \emph{Paths.Id} into \emph{{\bf h}Id}.

\subsubsection{Transitions}

\inputsnippets{GPaths/importationsa}

\subsubsection{Paths}

\inputsnippets{GPaths/pathsDefs}

\subsubsection{Main theorems about paths}

If $\beta$ is (strictly) accessible from $\alpha$, then
$\beta<\alpha$.

\inputsnippets{GPaths/pathToLT}

Constant index paths can be simulated with constant paths with larger index.

\inputsnippets{GPaths/Cor12}

If $\beta<\alpha$, then $\beta$ is accessible from $\alpha$
through some constant-index path.

\inputsnippets{GPaths/Lemma261}

Any constant-index path can be simulated by a ``standard'' path (with index incremented by 1 at each step).

\inputsnippets{GPaths/constantToStandard}

As a corollary, we relate ordinal inequality to standard paths.

\inputsnippets{GPaths/LTToStandard}
